---
title: "Course Faculty Course Format"
output: pdf_document
header-includes:
  - \usepackage{booktabs}
  - \usepackage{xcolor}
  - \definecolor{link}{rgb}{0, 0, 238}
---

```{r setup, include=FALSE}
library(magrittr)
library(knitr)
library(kableExtra)
opts_chunk$set(echo = FALSE)
```

<!-- ## List of instructor(s), with institutional affiliation(s) and e-mail address(es) -->

<!-- * Extended or mini-course format – Extended courses are 1–2 days in length and typically precede the Annual Meeting. Mini-courses are short courses, 4 hours in length, and are scheduled to take place during the Annual Meeting. -->

<!--   * AERA- VRLC (optional) Proposals are welcome for courses that will be streamed live online and recorded during the Annual Meeting for both in-person and virtual participants. These courses may be of varying length and format, contain modules that facilitate online viewing. Please indicate if the proposed course should be considered for the AERA-VRLC. Hyperlinks with course descriptions to previously recorded courses are permitted for VRLC course proposals. -->

```{r contactinfo}
data.frame(Presenters = c("Daniel Anderson", "Joshua Rosenberg"),
           Affiliation = c("University of Oregon", "University of Tennessee, Knoxville"),
           Email = c("daniela@uoregon.edu", "jrosenb8@utk.edu")) %>% 
  kable(booktabs = TRUE) %>% 
  kable_styling(position = "center")
```

This tutorial will be a **4-hour mini-course** on tools for conducting open and
reproducible research with R. It will overview the idea and importance of
reproducible research for educational researchers, cover R Markdown for weaving
text with code, and discuss *git*/*GitHub* for version control and
collaboration. Part of the benefit of R Markdown is that the syntax itself is
relatively straightforward (learning to code with R is much more difficult than
learning R Markdown), but is a powerful framework for presenting research
findings in a variety of formats, including static web pages, slides, technical
reports, and even APA-formatted journal articles. While the heart of our
presentation will focus on getting participants familiar and comfortable with R
Markdown and version control toward the ultimate goal of more open, 
transparent, and reproducible analysis workflows, we also spend some time
discussing these alternative output formats by way of motivating participants 
to continue learning beyond the mini-course. Both of the authors are 
experienced R users and have been using reproducible research principles in
their applied work for a number of years.

Dr. Anderson has taught R at the University of Oregon for each of the past two
years and is currently leading a five-course data science specialization for 
the University of Oregon's College of Education (see the current development 
\color{link}[here](https://github.com/uo-datasci-specialization)
\color{black}). In the classes Dr. Anderson teaches, he requires all work be
completed in a reproducible way. Similarly, he has provided training both to
faculty at the UO (for example, see \color{link}
[here](https://youtu.be/n-M2ivdofbo)\color{black}) and at other institutions 
in a consulting role (for example, see 
\color{link}[here](https://github.com/datalorax/FSU_June16)\color{black}). He
has also written multiple conference papers and led many conference
presentations using R Markdown, *GitHub*, and reproducible practices (for 
example, see \color{link} [his most recent presentation for NCME](https://github.com/datalorax/ncme_18)\color{black}).

Dr. Rosen recently completed his entire doctoral dissertation using R Markdown
and reproducible workflows with *GitHub* (see 
\color{link}[here](https://github.com/jrosen48/dissertation)\color{black}). He
has also given a \color{link}
[presentation on using R at Georgia Southern University](http://rpubs.com/jmichaelrosenberg/164105) \color{black} and a \color{link} [related presentation in the School of Criminal Justice at Michigan State University](/appendix/our-work/rosenberg-r_introduction_4-14-17.html) 
\color{black}.
  