---
title: "Course Faculty Course Format"
output: pdf_document
header-includes:
  - \usepackage{booktabs}
  - \usepackage{xcolor}
  - \definecolor{link}{rgb}{0, 0, 238}
---

```{r setup, include=FALSE}
library(magrittr)
library(knitr)
library(kableExtra)
opts_chunk$set(echo = FALSE)
```

# List of instructors

```{r contactinfo}
data.frame(Presenters = c("Daniel Anderson", "Joshua Rosenberg"),
           Affiliation = c("University of Oregon", "University of Tennessee, Knoxville"),
           Email = c("daniela@uoregon.edu", "jrosenb8@utk.edu")) %>% 
  kable(booktabs = TRUE) %>% 
  kable_styling(position = "center")
```

# Course format

This training will be a **4-hour mini-course** on tools for conducting open
and reproducible research with R. It will overview the idea and importance
of reproducible research for educational researchers, cover R Markdown for
weaving text with code, and discuss *git*/*GitHub* for version control and
collaboration. Part of the benefit of R Markdown is that the syntax itself
is relatively straightforward (learning to code with R is much more difficult
than learning R Markdown), but is a powerful framework for presenting research
findings in a variety of formats, including static web pages, slides, technical
reports, and even APA-formatted journal articles. While the heart of our
presentation will focus on helping participants to become familiar with and
comfortable using R Markdown and version control toward the ultimate goal of
more open, transparent, and reproducible analysis workflows, we also spend
some time discussing these alternative output formats by way of motivating
participants to continue learning beyond the mini-course. Both of the authors
are experienced R users and have been using reproducible research principles in
their applied work for a number of years.